\textbf{EECS 340: Assignment 1}

### 2020-01-26 assignment_1/article.tex
✨ Add pseudo-code for Problem 2(a).
✨ Add sketch answer to Problem 2(c) and Problem 2(d).

\documentclass[12pt]{article}
\usepackage{setspace}
\setstretch{1.1}
\usepackage{amsmath,amssymb, amsthm}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{footnotebackref}
\usepackage{url}
\usepackage{listings}
\usepackage[most]{tcolorbox}
\usepackage{inconsolata}
\usepackage[papersize={8.5in,11in}, margin=1in]{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{esint}
\usepackage{url}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{wasysym}
\newcommand{\inlinecode}{\texttt}
\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

@@

\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Bobby) CHEN, \inlinecode{zxc325}}
\date{Due on 01/27/2020, submitted on 01/26/2020 \\ EECS 340, Dr. Koyuturk}
\maketitle

@@

\section{Problem 2}
\subsection{(a)}
\subsection{(b)}
\subsection{(c)}
\subsection{(d)}

>>>>

\documentclass[12pt]{article}
\usepackage{setspace}
\setstretch{1.1}
\usepackage{amsmath,amssymb, amsthm}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{footnotebackref}
\usepackage{url}
\usepackage{listings}
\usepackage[most]{tcolorbox}
\usepackage{inconsolata}
\usepackage[papersize={8.5in,11in}, margin=1in]{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{esint}
\usepackage{url}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{wasysym}
\newcommand{\inlinecode}{\texttt}
\usepackage{etoolbox}
\usepackage{algorithm}
% \usepackage{algorithmic}
\usepackage[noend]{algpseudocode}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

@@

\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Robert) CHEN, \inlinecode{zxc325}}
\date{Due on 01/27/2020, submitted on 01/26/2020 \\ EECS 340, Dr. Koyuturk}
\maketitle

@@

\section{Problem 2}
\subsection{(a)}

\begin{algorithm}
\caption{TwoSum(A, B, n, x) with two pointers}\label{TwoSum}
\begin{algorithmic}[1]
\Procedure{}{}
\State $j \gets n-1$
\State $i \gets 0$
\While {$i < n \textbf{ and } j \geq 0$}
    \If {\textit{$A[i] + B[j] < x$}}
        \State $i \gets i + 1$
    \ElsIf {\textit{$A[i] + B[j] > x$}}
        \State $j \gets j - 1$
    \Else
        \State \Return $i, j$
    \EndIf
\EndWhile
\State \Return $False$
\EndProcedure
\end{algorithmic}
\end{algorithm}

\subsection{(b)}
\subsection{(c)}
If $A[i] + B[j] \neq x$, then it is impossible to have any combination $(a, b)$ where \\ $a \in \{A[0], A[1], ..., A[i-1], A[i]\}$ and $b \in \{B[j], B[j+1], B[j+2], ..., B[n-1]\}$ to \\be $a + b = x$ for all \textbf{iterarted} $i, j$ within the \inlinecode{while} loop.

Assume we get $A[i] + B[j] = k$ within an interation of the \inlinecode{while} loop, we either have $k < x$ or $k > x$ (assume $A[i] + B[j] \neq x$ because otherwise the loop will be terminated and the problem will be solved). Due to the sorted nature of array $A, B$, we must have:
\begin{gather}
    \underbrace{A[0] \leq A[1] \leq ... \leq A[i-1]}_{a} \leq A[i]  \ \ \ \Rightarrow a \leq A[i]\\
    \underbrace{B[n-1] \geq ... \geq B[j+2] \geq B[j+1]}_{b} \geq B[j] \ \ \ \Rightarrow b \geq B[j]
\end{gather}

Thus, we may infer the followings from the above two \textit{Equations}:
\begin{gather}
    \text{if } k < x: \ a + B[j] \leq A[i] + B[j]  \ \ \ \Rightarrow a + B[j] < x\\
    \text{if } k > x: \ A[i] + b \geq A[i] + B[j]  \ \ \ \Rightarrow A[i] + b > x
\end{gather}

It is a bit unintuitive about the case of $a' + b'$ for $a' \in \{A[0], A[1], ..., A[i-1]\}$ and $b' \in \{B[j+1], B[j+2], ..., B[n-1]\}$. But as the value of index $i$ ($j$) travels in an incremental (decremental) fashion in the bond of $\matthbb{Z+} \in [0, n)$; the index of $a'$ must be smaller than $i$, and the index of $b'$ must be greater than $j$. Thus, if there is any $a' + b' = x$, such loop would have been terminated immediately and we should not be able to reach to indexes $i, j$ in the \inlinecode{while} loop. Therefore, as we are now at the $i, j$ iteration of the \inlinecode{while} loop, this suggests there is no $(a', b')$ combination where $a' + b' = x$.

This together with \textit{Equation 10, 11}, we have proven the loop invariant as there will be no combination of $(a, b)$ where $a \in \{A[0], A[1], ..., A[i-1], A[i]\}$ and $b \in \{B[j], B[j+1], B[j+2], ..., B[n-1]\}$ to be $a + b = x$ for all \textbf{iterarted} $i, j$ within the \inlinecode{while} loop.

\subsection{(d)}
The worst case of this algorithm is when it returns \inlinecode{False}. In such case we wil have $i$ and $j$ travel the entire bond of $\matthbb{Z+} \in [0, n)$. The loop will execute $2n$ times, thus the run time is $O(n)$.
